Review of Assigned Readings

### 2018-01-04 paper/paper.tex
added first draft text in part 4 conclusion

%************************** Chapters 4 - Conclusion **************************
\section{Conclusion}
\label{sec:Conclustion}
(Insert text)

>>>>

%************************** Chapters 4 - Conclusion **************************
\section{Conclusion}
\label{sec:Conclustion}
Understanding, describing and predicting the current phenomenon of cryptocurrencies has been the objective of many researchers. A variety of methods and approaches have been applied und mixed results have been produced. Our goal for this seminar paper was to investigate the possibility of the existence of a correlation between twitter activity regarding bitcoin and the price evolution of bitcoin. After collecting hourly data for approximately 8 days we generated 2 time-series datasets and decided to perform a statistical analysis by using the Vector Autoregression (VAR) approach.\\

According to our regression results, changes in twitter activity due to more or less tweets about bitcoin have a very small and insignificant effect on future changes of bitcoin price. The validity of this statement was also verified and confirmed by the Granger causality test. At this point, however, it must be pointed out that only a small period of time has been considered in this analysis and the results cannot be generalized for the overall trend of cryptocurrencies in the recent time or for the future. We are also aware that we may have observed a period of abnormal behavior of bitcoin prices compared to the trend of the last months.\\

We encourage further research in the same direction as this paper and would be interested to see an analysis with observations over a longer period.
